Refinement of Thermostated Molecular Dynamics Using Backward Error Analysis

### 2019-02-26 rigid_bodies.tex
Dedication to Affonso Telles

\begin{acknowledgements}
The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).
\end{acknowledgements}

>>>>

\begin{acknowledgements}
This work is dedicated to the memory of Prof. Affonso da Silva Telles, a true scientist who played a major role in laying the foundation of Chemical Engineering research in Brazil.

The authors acknowledge the financial support provided by Petrobras (project code CENPES 16113).
\end{acknowledgements}
